\section{Applications}
\label{sec:applications}
\paragraph{OPRF applications} Before presenting applications specific to $\ioprf$s, we briefly
highlight that $\ioprf$s are maliciously-secure OPRFs and can consequently also be used to realize
maliciously-secure adaptive $k$-out-of-$n$ OT and oblivious keyword
search~\cite{adaptiveot,oks}. There, a sender encrypts each document
$i$ with a key $K_i$ that is derived from the document's keyword
$W_i$, i.e., $\kappa_i = \iprf_K(W_i)$. The sender sends resulting
ciphertexts to the receiver. Now, sender and receiver evaluate the
$\ioprf$ such that the receivers gets $\kappa=\ioprf_K(W)$ for a any
keyword $W$ the receiver is interested in. Using $\kappa$, the
receiver can decrypt all documents matching $W$. For more details, we
refer to \citet{oks}.  Note that if we ``structure'' keywords along
the paths of a binary tree, we can allow some party to derive, for
example, all keywords that start with the same prefix.

\paragraph{$\ioprf$ specific applications}
An immediate application specific to our $\ioprf$ (but not OPRFs!) is to force correct
compliance of clients in structured encryption by allowing them to
only query a contiguous path in the graph data.  This can be
accomplished by adding a layer of encryption inside of existing
structured encryption solutions such that each data element is also
encrypted with a key derived from one iteration of the $\ioprf$.
After the structured encryption protocol is complete, an $\ioprf$
protocol is executed which will allow for final decryption of the
results only if they are on a contiguous path.

To hide from the server which path is queried, the client can fetch
each node using Private Information Retrieval or maliciously secure
OT.
Also in scenarios with structured encryption, the $\ioprf$'s
delegation feature can be used to delegate control over well-specified
sub-trees of the original data to other parties. The delegate can then
act as a data owner on their sub-tree, serving requests from clients
with the same security property as the original data owner.

To understand the usefulness of $\ioprf$s, we now
consider a specific implementation of RFID tag authentication which
uses a limited form of structured encryption.


\input{rf}
\input{rf-delegation}

\subsection{Private Decision Tree Evaluation}
Another application where we can apply an $\ioprf$ is in the area of
private evaluation of decision trees.  There, the goal is to allow a
client holding a feature vector to query an outsourced decision tree
held by a server, resulting in the client receiving the machine
learning classification of their feature vector without the owner of
the decision tree learning what their input was. We refer to
\citet{schneidertree} for an overview.

The protocol by \citet{wu2016privately} accomplishes this with two
main techniques:

\begin{enumerate}[leftmargin=*]
\item Each node of the decision tree stores one value which will be
  compared against one feature of the client's feature vector.  To
  enable this, the client encrypts their feature vector with
  additively homomorphic encryption using the client's public key and
  sends ciphertexts to the server.  For each node of the tree, the
  server computes homomorphic DGK~\cite{dgk} comparisons ``$<$'' of
  one of the client's encrypted features with the specific node's
  value and sends encrypted comparison outcomes back to the client.
  Therewith, the client can identify the path in the tree and the leaf
  node corresponding to their input.

\item Once the correct leaf node is identified, the client uses
  oblivious transfer to retrieve it and compute the final
  classification.
\end{enumerate}

This protocol works for semi-honest clients, but it does not prevent
a malicious client from retrieving leaf nodes which do not actually
correspond to the result of their classification.  This is because the
server is not able to verify that the client traverses a contiguous
path in the tree or that the OT they perform corresponds to that path
if they did.
Consequently, \citeauthor{wu2016privately} suggest an augmented
version of the protocol that can handle malicious clients using a new
\emph{conditional oblivious transfer}, but a maliciously-secure
version could also be constructed simply by replacing OT with our
$\ioprf$.

Each node in the tree could be encrypted using keys derived
from the $\ioprf$ evaluation of their index, meaning that the client
would have to traverse a path in the tree all the way to the leaf in
order to decrypt it.  The only necessary modification for this
approach to work is a small number of additional ZKPs to ``bind'' the
results of the homomorphic evaluation to the input of the $\ioprf$.
When constructed this way, the client can use much more efficient
(maliciously secure) private information
retrieval~\cite{chang2004single} instead of the expensive conditional
OT designed by \citet{wu2016privately}.  For space reasons, we list only the main technical modifications necessary (in Appendix~\ref{app:dtrees}).
