\subsection{Delegation}
We achieve delegation for Construction~\ref{const:newprf} using the
following transformation algorithm $T$.
\begin{align*}
&\text{On input: }
(g,((\alpha_1,\beta_1),\ldots,(\alpha_\ell,\beta_\ell)),x^*_1\ldots{}x^*_i),
\\&T\text{ outputs: }
(g',((\alpha_{i+1},\beta_{i+1}),\ldots{},(\alpha_\ell,\beta_\ell))),
\text{where }{g'}=g^{\prod_{j=1}^{i}{\alpha_j^{x_j}\cdot\beta_j^{1-x_j}}}.
\end{align*}

Observe that $g'$ is effectively a precomputed partial-$\iprf$ for input
$(x^*_1\ldots{}x^*_i)$.  So, if party $P_1$ sends
$({g'},((\alpha_{i+1},\beta_{i+1}),\ldots{},(\alpha_\ell,\beta_\ell)))$
to $P_2$, $P_2$ can then compute $\iprf$ outputs
$(v_{i+1},\ldots,v_\ell)$ for any input string $x=(x_1\ldots{}x_\ell)$
which has $(x^*_1\cdots{}x^*_i)$ as a prefix by computing
$v_{k}={g'}^{{\prod_{j={i+1}}^k{\alpha_j^{x_j}\cdot\beta_j^{1-x_j}}}}$.

\begin{lemma}
Construction~\ref{const:newprf} with transformation $T$ is a
delegatable $\iprf$.
\end{lemma}

\begin{proof}
  We prove this by straightforward reduction.  Let $\iprf_K$ be
  Construction~\ref{const:newprf} for inputs $x$ of length $\ell+1$
  bits, and let $\widehat{\iprf}_{\widehat{K}}$ be
  Construction~\ref{const:newprf} for inputs $x$ of length $\ell$
  bits.  Let prefix $x^*$ be any length $\ell$ bit string, and $K$ and
  $\widehat{K}$ are randomly chosen keys.

  Assume there exists distinguisher $\D$ which can distinguish the
  first $\ell$ outputs from $\iprf_K$ with a prefix different from $x^*$
  with non-negligible probability from $\ell$ random bit strings.

  We build distinguisher $\D'$ who will be able to distinguish the
  $\ell$ outputs from $\widehat{\iprf}_{\widehat{K}}$ from $\ell$
  randomly chosen bit strings.

\begin{enumerate}
\item If $\D$ queries for delegation of length $\ell$ prefix $x^*$,
  $\D'$ will query their challenger for $x^*$ and will get back $z$
  which is either $(v_1,\ldots,v_\ell)=\iprf_K(x^*)$ or $\ell$ random
  bit strings $(r_1,\ldots,r_\ell)$.
\item $\D'$ generates a random pair
  $(\alpha_{\ell+1},\beta_{\ell+1})\getr(\Z_p)^2$.  It computes
  transformation $(g'=z, (\alpha_{\ell+1},\beta_{\ell+1}))$ and sends it
  to $\D$.
\item When $\D$ queries for $x$ with a different prefix than $x^*$, $\D$
forwards $x$ to their challenger, forwards the response to $\D$ and
outputs whatever $\D$ outputs.
  
\end{enumerate}  
If $\D'$ is receiving the output of a $\widehat{\iprf}_{\widehat{K}}$,
then the values it gives to $\D$ will be identifically distributed to
correct outputs of a delegated $\iprf$, with the effective key of $K$
concatenated with the random $(\alpha_{\ell+1}, \beta_{\ell+1})$.  If
$\D'$ is receiving random strings $(r_1,\ldots,r_\ell)$, then $\D$ is also
getting random strings.  Therefore, $\D$'s view is distributed
identically to its distinguishing game. If $\D$ has a non-negligible advantage in distinguishing, then
$\D'$ will have the same advantage in distinguishing $\iprf$ output from random strings.
\end{proof}
