\subsubsection{Proof of Construction~\ref{const:ioprf}}
\label{mainproof}
We now turn to our main proof, showing that
Construction~\ref{const:ioprf} is a secure $\ioprf$. We prove in the
hybrid model, using ZK hybrids with their abbrevations as introduced
in the previous section.  Recall that, in the hybrid model, ZK hybrids
are run by separate trusted third parties. Yet, during simulation, it
is the simulator who takes the role of the TTP and thus automatically
gets the adversary's inputs and can also cheat, see \citet{howto} for
details.

\begin{theorem}
  Assume that Construction~\ref{const:newprf} is an iterative
  pseudo-random function family $\iprf_K(\cdot)$.  Then,
  Construction~\ref{const:ioprf} is an $\ioprf$, realizing
  functionality $\fioprf$ in the
  $\left(\fzk{enc},\fzk{pop},\fzk{bit},\fzk{sum},\fzk{ExR}\right)$
  hybrid-model.
\end{theorem}

\begin{proof}
  First, observe that Construction~\ref{const:ioprf} is correct. Let
  $x$ be the receiver's input, and $K$ the key chosen by the
  sender. If both sender and receiver are honest, then the sender
  outputs nothing, and the receiver outputs
  $(v_1,\ldots,v_\ell)=\iprf_K(x)$. Thus, we focus on proving security
  and build simulators for two cases: one where $S$ is compromised,
  and one where $R$ is compromised.

  We will show that a simulator $\myS$ can be constructed from both
  the perspective of $S$ and $R$ such that the adversary $\A$'s view
  is indistinguishable from real executions of the protocol.  Thus we
  show that neither a compromised $S$ nor a compromised $R$ learn
  anything from the real execution of Construction~\ref{const:ioprf}
  beyond what is specified by the ideal functionality in
  Figure~\ref{idealioprf}.

  In our presentation below, we will use the term
  ``$\myS$ \emph{aborts''} as a shorthand for $\myS$ sending \abort to
  the TTP, simulating its party aborting to $\A$, and then outputting
  whatever $\A$ outputs.

In both cases below, the simulator will faithfully act as a verifier
  for ZKPs when interacting with $\A$ as necessary, aborting if the
  proof does not verify correctly. We omit these messages for
  readability since they require no special knowledge or behavior from
  the simulator. Our strategy will broadly be to:

\begin{itemize}[leftmargin=*]
  \item Replace Elgamal ciphertexts sent by $R$ with encryptions of
  zero (arbitrarily chosen).  Due to Elgamal's IND-CPA property, these
  ciphertexts will be indistinguishable from the real protocol for
  $\A$.  Since $S$ reveives no output from the real execution of the
  protocol, ciphertexts do not have to conform to any
  expectations.

\item Replace computation of $X_i$ and $Y_i$ by $S$
  in the real protocol with an encryption of the output of the
  $\ioprf$ received from the TTP.  $\myS$ does not know
  $K_i=(\alpha_i,\beta_i)$ and so cannot faithfully compute $X_i$ or
  $Y_i$, but it knows from the TTP what output $v_i$
  should. Consequently, $\myS$ crafts these values accordingly to
  simulate the real protocol and ``cheat'' in ZKPs where $\myS$ acts
  as the prover (see, e.g., \S~\ref{sec:extraction}).
\end{itemize}

Together, this will allow the simulator to generate a view which is
indistinguishable from a real execution, \ignore{\fixme{we said that
in the first paragraphs}while having now knowledge beyond that given
by the TTP,} thus proving that our construction is secure according to
Definition~\ref{def:ioprf}.

Note that also for all ZKPs with $\myS$ as a prover, $\myS$ acts as
the TTP and ``cheats'' to convince $\A$.  In many instances, $\myS$
could honestly prove to $\A$, so ``cheating'' is not really. Yet, for
ease of exposition, we assume that all proofs are simulated this way.
  
\vskip 1eX\noindent{\bf Case 1:} We assume that $\A$ has compromised
$S$ and build simulator $\myS$ taking the role of $S$ in the ideal
world, internally simulating a receiver to $\A$ which it only has
black box access to.

$\myS$ starts $\A$ and receives $2\ell$ commitments
$(\com(\alpha_i),\com{}(\beta_i))$ from $\A$. $\myS$ also receives
corresponding $(\alpha_i,\beta_i)$ together with random coins from
$\fzk{pop}$ sent from $\A$ to $\fzk{pop}$. If these do not match the
commitments, $\myS$ \emph{aborts}.
 

$\myS$ also
generates an Elgamal key pair $(sk, pk)$, sends
$pk$ to $\A$, and simulates $\fzk{enc}$.  Also, $\myS$ generates
$V_0=\enc_{pk}(0)$ and $D_0=\enc_{pk}(0)$, sends them to $\A$, and
simulates $\fzk{enc}$.
    
\noindent{}During the $i^\text{th}$ round,
  \begin{enumerate}[leftmargin=*]
  \item $\myS$ sends two independent commitments of zero and simulates
  $\fzk{bit}$ and $\fzk{sum}$.

  \item $\myS$ also computes and sends $(c_i,c'_i,d_i,d'_i)$, all
    encryptions of zero, to $\A$ and simulates
    $\fzk{ExR}$.

  \item $\myS$ receives $(X_i, Y_i)$ from $\A$ as well as
    $(\alpha'_i,\beta'_i)$ and random coins from $\fzk{ExR}$. If
    $\alpha_i\neq\alpha'_i$ or $\beta_i\neq\beta'_i$ or if random
    coins do not match computations specified in
    Construction~\ref{const:ioprf}, then $\myS$ \emph{aborts}. If they
    match, $\myS$ forwards $K_i=(\alpha_i,\beta_i)$ to the TTP.
   
  \item $\myS$ sends $P_i,P'_i,Q_i,Q'_i$, encryptions of zero, to $\A$
    and simulates $\fzk{ExR}$.
    
  \end{enumerate}
  $\myS$ outputs what $\A$ outputs.
During simulation, whenever $\A$ aborts, $\myS$ also \emph{aborts}.

\paragraph{Indistinguishable views} In the protocol, there are three types
of messages that $\myS$ sends to $\A$: Pedersen commitments, Elgamal
ciphertexts, and ZKP messages.  All of the Elgamal ciphertexts are
freshly encrypted (or re-encrypted) using fresh randomness.  They are
thus indistinguishable from any other Elgamal encryption, regardless
of any a priori knowledge that $\A$ might have.  As stated above, the
ZKPs are simulated and are thus also indistinguishable from a real
execution.  Finally, the commitments are perfectly hiding and are
never revealed during the protocol, so they are also indistinguishable
from the commitments of a real execution.

\vskip
1eX\noindent{\bf Case 2:} We assume that $\A$ has compromised $R$ and
build simulator $\myS$ as follows.

$\myS$ starts $\A$.
 $\myS$ randomly selects $\ell$ pairs $(\alpha'_i,\beta'_i)\getr(\Z_p)^2$,
  commits to them, sends commitments to $\A$, and proves knowledge of
  $(\alpha'_i,\beta'_i)$ using $\fzk{pop}$.

$\myS$ receives $pk$ from $\A$ and $(sk',pk')$ from
$\fzk{enc}$ which $\A$ has sent. If $pk\neq{}pk'$ or
$g_1^{sk'}\neq{}pk$, $\myS$ \emph{aborts}.  Also, $\myS$ receives
$(V_0,D_0)$ from $\A$ and $\A$'s random coins from $\fzk{enc}$. If
random coins do not match encryptions of $1$ ($V_0$) or $0$ ($D_0$),
$\myS$ \emph{aborts}.

\noindent{}During the $i^\text{th}$ round, 
\begin{enumerate}[leftmargin=*]
\item $\myS$ receives $(\com(x_i)$, $\com(1-x_i))$ from $\A$ and
  $(x'_i,1-y'_i)$ with the commitments' random coins from
  $\fzk{bit}$. If $x'_i$ or $1-y'_i$ and random coins do not match
  commitments, $\myS$ \emph{aborts}. In the same way, $\myS$ receives
  $z$ and a random coin for the commitment from sum hybrid
  $\fzk{sum}$. If $z\neq{}1$ or $z\neq{}x'_i+1-y'_i$ or the random
  coin does not match the commitment, $\myS$ \emph{aborts}. If
  everything matches, $\myS$ knows $\A$'s input $(x_i,1-x_i)$.

  $\myS$ receives $(c_i,c'_i,d_i,d'_i)$ from $\A$ and random coins and
  $(x'_i,1-y'_i)$ from $\fzk{ExR}$. If $(x'_i,1-y'_i)$ do not match
  the ones from the previous step or if any of the computations do not
  match $(c_i,c'_i,d_i,d'_i)$, $\myS$ \emph{aborts}.

  $\myS$ computes $(T_i,U_i)$ as in Construction~\ref{const:ioprf}.
  
\ignore{   Crucially, as $\myS$ knows $x_i$,
  they also know which of $T_i$ or $U_i$ contains the encryption of
  previous $\iprf$ output $v_{i-1}$ and which contains an encryption
  of $0$. If $x_i=1$, then $T_i$ contains the encryption of $v_{i-1}$
  (encryption of $1$ for $v_0$), and $U_i$ contains an encryption of
  $0$. If $x=0$, it is the other way around.}

\item $\myS$ queries the TTP for $x'_i$ and gets back $v_i$. If
  $x_i=1$, $\myS$ sets $X_i\leftarrow\enc_{pk}(v_i)$ and
  $Y_i\leftarrow\enc_{pk}(0)$.  If $x_i=0$, $\myS$ sets
  $X_i\leftarrow\enc_{pk}(0)$ and $Y_i\leftarrow\enc_{pk}(v_i)$.
  $\myS$ sends $(X_i,Y_i)$ to $\A$ and \emph{cheats} in $\fzk{ExR}$,
  convincing $\A$ that $(X_i,Y_i)$ are the result of raising $T_i$ and
  $U_i$ to $\alpha'_i$ and $\beta'_i$ and then re-encrypting.
  
\ignore{
  If $x_i = 1$,
meaning that $T_i$ contains the input from $\A$ that should be
included in the PRF, then $\myS$ computes $X_i = \enc_pk(y)$ and $Y_i = \enc_pk(0)$. If $x_i = 0$ it computes $Y_i
= \enc_pk(y)$ and $X_i = \enc_pk(0)$.  In either case, it also
``cheats'' the proofs $\fzk{pop}$ and $\fzk{ExR}$ by rewinding after
receiving the challenge and producing a correct commitment to match
the challenge.  This is necessary because $\myS$ does not know
$\alpha$ or $\beta$, only the final output of the $\ioprf$.
}

\item Finally, $\myS$ receives $(P_i,P'_i,Q_i,Q'_i)$ from $\A$ and
  random coins and $(x'_i,1-y'_i)$ from $\fzk{ExR}$. Again, $\myS$
  verifies correct computation of $(P_i,P'_i,Q_i,Q'_i)$ and whether
  $(x'_i,1-y'_i)$ match previously received values. If anything does
  not match, $\myS$ \emph{aborts}.

  $\myS$ computes $(V_i,D_i)$ as in Construction~\ref{const:ioprf}.
  
\end{enumerate}
  $\myS$ outputs what $\A$ outputs.
During simulation, whenever $\A$ aborts, also $\myS$ \emph{aborts}.

\paragraph{Indistinguishable views} As before, the commitments are
perfectly hiding and are not revealed and so are indistinguishable
from commitments of a real protocol execution.  ZKPs are also
simulated as before and are indistinguishable for the same reason.

The only part that is different in this case is the returned values of
$X_i$ and $Y_i$, which have to decrypt to the correct output of the
$\ioprf$ in order to match the real protocol.  Fortunately, $\myS$ can
query the TTP for the correct output and generate encryptions that
match that output.  In the real protocol, $S$ reencrypts $X_i$ and
$Y_i$ before returning them to $R$, and so they are indistinguishable
from the fresh encryptions generated by $\myS$.
\end{proof}
As $R$ verifies whether $S$ sends the same commitments to
$(\alpha_i,\beta_i)$ during multiple executions of
Construction~\ref{const:ioprf}, we trivially achieve verifiability.
